---
title: My dynamic report
output: html_fragment
---

## Exploring Appliance Usage and Time Patterns
This report explores the dataset of household appliance usage over time. The dataset includes the following key variables:

- **timestamp**: The time when the data was recorded.
- **time_of_completion**: The time at which the task was completed.
- **time_period**: The time period during which the appliance usage occurred.
- **appliances_used**: A list of appliances used during the recorded period.
- **total_time_hours**: The total duration of appliance usage in hours.

The objective of this analysis is to understand the distribution of appliance usage across different time periods and identify patterns related to the number of appliances used.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css echo=FALSE}
h2{color:purple}
h3{color:orange}
body{font-size:12pt; color: black
}
```

```{r}
# Import data
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQ7dXYzqjRIlKT8V1lk9EPfupxy_vnE5OZf3mQxCO2hZJ7J1qGscymtOGDXJEboMo6Iadpyv8kGZ6Ve/pub?output=csv")
```


```{r}
# Renamed colums
latest_data <- logged_data %>% 
  rename(
    timestamp = Timestamp,
    time_of_completion = `X..Time.of.Completion`,
    time_period = `X...Current.Time.Period`,
    appliances_used = `X..Appliances.Used`,
    total_time_hours = `X....Total.time.of.use.of.all.appliance..hours.`
  )
```


```{r}
### Summary values
## The mean and maximum of the total time spent using appliances are calculated and printed.
mean_time <- mean(latest_data$total_time_hours, na.rm = TRUE)
max_time <- max(latest_data$total_time_hours, na.rm = TRUE)
```

### Print dynamic comments
```{r}
paste("The average total time of appliance usage is", round(mean_time, 2), "hours.")
paste("The maximum recorded total time of appliance usage is", round(max_time, 2), "hours.")
```

### Draw a plot
#### The first chart shows the distribution of time periods (Morning, Afternoon, etc.).
```{r}
ggplot(latest_data, aes(x = time_period)) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(title = "Distribution of Appliance Usage by Time Period", x = "Time Period", y = "Frequency") + 
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  geom_text(stat='count', aes(label=..count..), vjust=-0.5)
```


#### Bar chart 2: Frequency of appliances used
```{r}
latest_data$appliance_count <- str_count(latest_data$appliances_used, ",") + 1
ggplot(latest_data, aes(x = appliance_count)) +
  geom_bar(fill = "pink", color = "black") +
  labs(title = "Frequency of Appliances Used", x = "Number of Appliances", y = "Count") + 
  theme(axis.text.x = element_text(hjust = 1)) + 
  geom_text(stat='count', aes(label=..count..), vjust=-0.5) +
  scale_color_brewer(palette = "Dark2") +
  theme_minimal()
```

 






